Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with stable Branching

### 2019-03-06 supCLT.tex
supCLT.tex: 0306

@@

    %[CLT for Super-OU processes]

@@

    %{Stable Central Limit Theorems for Super OU Processes with Stable Branching}

@@

    %{Renming Sond\\

@@

%ZS: I changed all "branching rate regime" to "branching rate regime" below.

@@

	%Consider a super Ornstein-Uhlenbeck processes (super-OU process) $(X_t)_{t\geq 0}$ with branching mechanism 
    Consider a $(\xi, \psi)$-superprocess $(X_t)_{t\geq 0}$ where the spatial motion $\xi$ is an Ornstein-Uhlenbeck process on $\mathbb R^d$  which has generator $L = \frac{1}{2}\sigma^2\Delta - b x \cdot \nabla$ with $\sigma, b >0$, and the
    branching mechanism $\psi$ takes the form close to
	$\psi(z)=-\alpha z +\rho z^2+ \eta z^{1+\beta}$ with $\alpha>0$, $\rho\ge 0$, $\eta>0$ and $\beta\in (0, 1)$ in some sense.

@@

    %Conditioned on no-extinction, we establish some spatial central limit theorems for $\langle f, X_t \rangle$ in three different regimes: 

@@

    %In the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/\|X_t\|^{\frac{1}{1+\beta}}$ converges weakly to a $(1+\beta)$-stable random variable.
    %In the critical branching rate regime  $\alpha\beta= \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/(t\|X_t\|)^{\frac{1}{1+\beta}}$ converges weakly another $(1+\beta)$-stable random variable.
    %In the large branching rate regime  $\alpha\beta> \kappa_f b(1+\beta)$, we first prove that $e^{-(\alpha-\kappa(f)b)t}\langle f,X_t\rangle$ converges almost surely and in $L^{1+\gamma}$, for any $\gamma \in (0,\beta)$, and then established a central limit theorem, which says that, after proper centering and scaling, $\langle f,X_t\rangle$ again converges weakly to a $(1+\beta)$-stable random variable.

@@

%MOVED BELOW
    %Denote by $\mathcal B(\mathbb R^d, \mathbb R)$ the space of all $\mathbb R$-valued Borel measurable functions on $\mathbb R^d$.
    %Denote by $\mathcal B(\mathbb R^d, \mathbb R_+)$ the space of all $\mathbb R_+$-valued Borel measurable functions on $\mathbb R^d$.
    %Denote by $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
    %For each $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ and $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integrals make sense.
    %For each $\mu \in \mathcal M(\mathbb R^d)$, write $\|\mu\| = \langle 1, \mu\rangle$.
    %We say a real-valued measurable function $f:(t,x)\mapsto f(t,x)$ on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if for each $t\in \mathbb R_+$, we have
%\[
    %\sup_{s\in [0,t],x\in \mathbb R^d} |f(s,x)|<\infty.
%\]
%END MOVED BELOW

@@

    %where $\sigma$ and $b$ are positive constants.

@@

%DELETED
	%It is known that $\alpha, \rho$ and $\pi$ are uniquely determined by the function $\psi$.
%END DELETED
	We refer to $\pi$ the \emph{L\'evy measure} of the branching mechanism $\psi$.
%MOVED FROM ABOVE

@@

    We say a real-valued measurable function $f:(t,x)\mapsto f(t,x)$ on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if for each $t\in \mathbb R_+$, we have

@@

%END MOVED FROM ABOVE
       We say an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ 

@@

    Recently, there have been quite a few papers on laws of large numbers for superdiffusions. In \cite{Englander2009Law, EnglanderWinter2006Law, EnglanderTuraev2002A-scaling}, some weak laws of large numbers (convergence in law or in probability) were established. The strong law of large numbers for superprocesses was first studied in \cite{ChenRenWang2008An-almost}, 
    %followed by \cite{ChenRenSongZhang2015Strong-law, ChenRenYang2019Skeleton, EckhoffKyprianouWinkel2015Spines,KouritzinRen2014A-strong,LiuRenSong2013Strong, Wang2010An-almost}. 
    %The setups of the papers mentioned above are  different. 
    followed by \cite{ChenRenSongZhang2015Strong-law, ChenRenYang2019Skeleton, EckhoffKyprianouWinkel2015Spines,KouritzinRen2014A-strong,LiuRenSong2013Strong, Wang2010An-almost} under different settings. 
    For a good survey on recent developments in laws of large numbers for branching Markov processes and superprocesses, see \cite{EckhoffKyprianouWinkel2015Spines}.

    %In this paper, we focus on limit results for the super-OU process $X$.
    %The strong law of large numbers of $X$ can be stated as follows: 
    The strong law of large numbers of the above super-OU process $X$ can be stated as follows: 
    Under some conditions on the branching mechanism $\psi$ (these conditions are satisfied under our assumptions 1 and 2, below), there exists an $\Omega_0$ of $\mathbb{P}_\mu$-full probability for every $\mu\in\mathcal M(\mathbb R^d)$ such that on $\Omega_0$, 
    %for every Lebesgue-almost everywhere continuous bounded $f\in\mathcal B(\mathbb R^d, \mathbb R_+)$,
    for every Lebesgue-almost everywhere continuous bounded non-negative function $f$ on $\mathbb R^d$, 
    we have
    $\lim_{t\to\infty}e^{-\alpha t}\langle f, X_t\rangle=H_\infty\langle f,\phi_0\varphi\rangle $, 
    %where  $H_\infty=\lim_{t\to\infty}e^{-\alpha t}\|X_t\|$, and the convergence also holds in $L^1(\mathbb P_\mu)$, see \cite[Theorem 2.13 \& Example 8.1]{ChenRenYang2019Skeleton} and \cite[Theorem 1.2 \& Example 4.1]{EckhoffKyprianouWinkel2015Spines}.
    where $H_\infty$ is the limit of the non-negative martingale $e^{-\alpha t}\langle 1,X_t\rangle$ and $\phi_0$, $\varphi$ are functions which will be introduced in  \eqref{eigenfunction} and \eqref{invariantdensity} below.
    See \cite[Theorem 2.13 \& Example 8.1]{ChenRenYang2019Skeleton} and \cite[Theorem 1.2 \& Example 4.1]{EckhoffKyprianouWinkel2015Spines}.

    %In this paper, we will establish some spatial central limit theorems for the super-OU process $X$ above.  
    In this paper, we will establish some spatial central limit theorems (CLT) for the super-OU process $X$ above. 
%NEW ADDED
    Our key assumption is that the corresponding branching mechanism $\psi(z)$ takes the form of $-\alpha z +\rho z^2+ \psi_1(z)$ where $\psi_1$ is close to $\eta z^{1+\beta}$ with $\eta>0$ and $\beta\in (0, 1)$ in some sense.
%END ADDED
    %More precisely, we want to find 
    We want to find
    %$F_t$ and $G_t$ such that
    $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ such that
\[
    \frac{\langle f, X_t \rangle -G_t}{F_t}
\]
    converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, 
    %for some test functions $f$.
    for some testing functions $f$.
    %It turns out that the normalization $F_t$ depends on the branching rate regimes determined by the sign of $\alpha\beta-\kappa_f b (1+\beta)$, where $\kappa_f$ is the order of $f$ in the spectral decomposition in terms of the spectrum of $L$.
    It turns out that there are three regimes of different behavior of this CLT depending on the sign of $\alpha\beta-\kappa_f b (1+\beta)$: the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$; the critical branching rate regime $\alpha\beta = \kappa_f b(1+\beta)$; and the large branching rate regime $\alpha\beta > \kappa_f b(1+\beta)$. Here, $\kappa_f$ is the order of $f$ in the spectral decomposition in terms of the spectrum of $L$. 
%ADDED
    Note that, under the settings of this paper, $\langle f,X_t\rangle$ typically have infinite second moment.
%END ADDED

    %There are many papers studying central limit theorems for branching processes, branching diffusions and superprocesses.
    There are many papers studying central limit theorems for branching processes, branching diffusions and superprocesses under finite second moment condition.
    See
    \cite{Heyde1970A-rate, HeydeBrown1871An-invariance, HeydeLeslie1971Improved} for supercritical Galton-Watson processes, 
    %see \cite{KestenStigum1966Additional,KestenStigum1966A-limit} for supercritical multi-type Galton-Waston processes, 
    \cite{KestenStigum1966Additional,KestenStigum1966A-limit} for supercritical multi-type Galton-Watson processes,
    \cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some} for supercritical multi-type continuous time branching processes and \cite{AsmussenHering1983Branching} for general supercritical branching Markov processes under certain conditions.
    In \cite{AdamczakMilos2015CLT}, 
    %Adamcazk and Milo\'s 
    Adamczak and Milo\'s 
    proved some central limit theorems for supercritical branching Ornstein-Uhlenbeck processes with binary branching mechanism and in \cite{Milos2012Spatial} Milo\'s proved some central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition.
    These two papers made connections between CLT and what they call branching rate regimes.
    In \cite{RenSongZhang2014Central}, Ren, Song and Zhang proved some central limit theorems for supercritical super-OU processes with branching mechanisms satisfying only a second moment.
    %Moverover, 
    Moreover,
    compared with the results in \cite{AdamczakMilos2015CLT,Milos2012Spatial}, the limit distributions in \cite{RenSongZhang2014Central} are non-degenerate.
    In \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central},
    Ren, Song and Zhang also established a series of central limit theorems for a large class of general supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms.
    The functional version of the central limit theorems was established in \cite{Janson2004Functional} for supercritical multitype branching processes, and  in \cite{RenSongZhang2017Functional} for supercritical superprocesses.

    %All central limit results described above hold for systems with branching mechanisms with finite variance.
    %It is natural to ask whether there are counterparts of the central limit theorems for branching Markov processes and superprocesses with branching mechanisms of infinite variance.
    There are also many limiting theory for branching processes and branching Markov processes with branching mechanisms of infinite second moments.
    Heyde \cite{Heyde1971Some} established a central limit type  theorem for Galton-Watson process 
when the offspring distribution
    %belongs to the domain of a stable law of index $\alpha\in (1, 2]$, 
    belongs to the domain of attraction of a stable law of index $\alpha\in (1, 2]$,
    and   proved that the limit law is  a stable law. Similar results  for supercritical multi-type Galton-Watson processes and supercritical  continuous time branching processes,  
under some $p$-th ($p\in(1,2]$) moment condition on the offspring distribution,
    were given in Asmussen \cite{Asmussen76Convergence}.
    Recently,   Marks and Milo\'s \cite{MarksMilos2018CLT}
    considered the limit behavior of supercritical branching Ornstein-Uhlenbeck processes with a special stable branching law. 
    %They established some central limit theorems in small and critical branching rate regimes, but they did not prove any central limit theorem type result in the large branching rate regime.
    They established some central limit theorems in small and critical branching rate regimes, but they did not prove any central limit theorem type result in the large branching rate regime.
%NEW ADDED
    We also mention here that very recently \cite{IksanovKoleskoMeiners2018Stable-like} considered the stable fluctuations of Biggins' martingales in the context of branching random walks and \cite{RenSongSun2018Limit} considered the asymptotic behavior of a class of critical superprocesses with spatially dependent stable branching.
%END NEW ADDED

%NEW ADDED
    As far as we know, this paper is the first one in the literature on establishing CLT for supercritical superprocesses without the second moment condition.
%END added
%DELETED
    %In this paper, we consider a class of super-OU processes with a general stable branching mechanism.
    %For small and critical branching rate regimes, we obtain central limit theorems which are similar to the corresponding results for branching Ornstein-Uhlenbeck processes in \cite{MarksMilos2018CLT}.
    %For large branching rate regime, we not only prove an almost sure convergence result as in \cite{MarksMilos2018CLT}, we also prove a central limit theorem type result.
%END DELETED

%DELETED    
    %For recent works on limit results (strong law of large numbers and central limit theorems) for branching diffusions and general branching Markov processes, we refer to \cite{BansayeDelmasMarsalleTran2011Limit, ChenRenSongZhang2017Law, EnglanderHarrisKyprianou2010Strong, GrubelKabluchko2016A-functional, RenSongZhang2015Central} and references there in.
%END DELETED

%    {\bf ZS: I think this subsection should be extended with more literatures like:
%    \cite{AdamczakMilos2014U-statistics},
 %   \cite{EckhoffKyprianouWinkel2015Spines},
%    \cite{EnglanderHarrisKyprianou2010Strong},
%    \cite{IksanovKabluchko2016A-central},
%    \cite{LiuRenSong2013Strong},
%    \cite{Wang2018Central},
%    \cite{IksanovKoleskoMeiners2018Stable-like},
%    \cite{IksanovKoleskoMeiners2018Fluctuations},
%    \cite{GrubelKabluchko2016A-functional},
%    \cite{Heyde1970A-rate},
%    \cite{Heyde1971Some},
%    \cite{HeydeBrown1871An-invariance},
%    \cite{HeydeLeslie1971Improved},
%    \cite{BansayeDelmasMarsalleTran2011Limit},
%    \cite{EnglanderWinter2006Law},
%    \cite{Englander2009Law},
%    \cite{Janson2004Functional},
%    \cite{ChenRenWang2008An-almost},
%    \cite{Wang2010An-almost},
%    \cite{HartungKlimovsky2018The-phase},
%    \cite{BansayeDelmasMarsalleTran2011Limit},
%    \cite{Le2019Long}.
%
 %   YX: I have added some parts which are related to references listed above. But I did not cite  \cite{AdamczakMilos2014U-statistics}, \cite{HartungKlimovsky2018The-phase} and \cite{Wang2018Central} since these are not closely related to our paper. I did not cite \cite{HeydeLeslie1971Improved}--\cite{IksanovKoleskoMeiners2018Stable-like} since these are about central limit theorems for Biggin's martingales.
%}
\subsection{Main results}
\label{sec: main results}{}

%MOVED BELOW	
	%Denote by $\Gamma$ the gamma function.
%For any $\sigma$-finite signed measure $\mu$, we use $|\mu|$ to denote the total variation measure of $\mu$.
%END MOVED BELOW
	We will always assume that the following Assumption holds.
\begin{asp}
\label{asp: Greys condition}
	The branching mechanism satisfies the Grey's condition, i.e. there is some constant $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$ and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
\end{asp}
%MOVED FROM ABOVE
    For each $\mu \in \mathcal M(\mathbb R^d)$, write $\|\mu\| = \langle 1, \mu\rangle$.
%END MOVED FROM ABOVE
	It is known (see \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations} for example) that, under Assumption \ref{asp: Greys condition}, 
	the \emph{extinction event} 
	$D:=\{\exists t\geq 0,~\text{s.t.}~\|X_t\|=0\}$ has a positive probability, with respect to $\mathbb P_\mu$ for each  $\mu \in \mathcal M(\mathbb R^d)$.
    In fact,
\begin{equation}
    \mathbb{P}_{\mu} (D)
    = e^{-\bar v \|\mu\|},
    \quad \mu\in \mathcal M(\mathbb R^d),
\end{equation}
    where
\[
	\bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\} \in (0,\infty)
\]
	is the largest root of $\psi$.

%MOVED FROM ABOVE
    Denote by $\Gamma$ the gamma function.
For any $\sigma$-finite signed measure $\mu$, we use $|\mu|$ to denote the total variation measure of $\mu$.
%END MOVED FROM ABOVE    
    In this paper, we will also assume the following:
\begin{asp}
\label{asp: branching mechanism}
    There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that
\begin{equation}
\label{eq: asp of branching mechanism}
    \int_{(1,\infty)}y^{1+\beta +\delta}~\Big|\pi(dy)-\frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| <\infty,
\end{equation}
	for some $\delta > 0$.
\end{asp}
    %{\bf Jianjie: do we need to emphasize that $\delta\in (0,1-\beta)$ such that $1+\beta+\delta<2$.}
    %ZS: It is done by Remark 1.1. 
	We will show in Subsection \ref{sec: branching mechanism} that if Assumption \ref{asp: branching mechanism} holds, then $\eta$ and $\beta$ are uniquely determined by the L\'evy measure $\pi$.
	In the reminder of the paper, we will always use $\eta,\beta$ to denote the constants corresponding to $\pi$.
\begin{rem}
\label{rem: small enough delta}
	Note that $\delta$ is not uniquely determined by $\pi$.
	In fact, if $\delta>0$ is a constant such that \eqref{eq: asp of branching mechanism} holds, then replacing $\delta$ by any smaller positive number, \eqref{eq: asp of branching mechanism} still holds.
	Therefore, Assumption \ref{asp: branching mechanism} is equivalent to the following statements: There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that, for each small enough $\delta>0$, \eqref{eq: asp of branching mechanism} holds.
\end{rem}

>>>>

%supCLT-2.tex 2019/03/05 by Renming
%supCLT.tex 2019/03/04 by Zhenyao

@@

@@

@@

@@

@@

  %  Consider a $(\xi, \psi)$-superprocess $(X_t)_{t\geq 0}$ where the spatial motion $\xi$ is an Ornstein-Uhlenbeck process on $\mathbb R^d$  which has generator $L = \frac{1}{2}\sigma^2\Delta - b x \cdot \nabla$ with $\sigma, b >0$, and the
%    branching mechanism $\psi$ takes the form close to
%	$\psi(z)=-\alpha z +\rho z^2+ \eta z^{1+\beta}$ with $\alpha>0$, $\rho\ge 0$, $\eta>0$ and $\beta\in (0, 1)$ in some sense.
Let $\xi$ be an Ornstein-Uhlenbeck process on $\mathbb R^d$ with generator $L = \frac{1}{2}\sigma^2\Delta - b x \cdot \nabla$, where $\sigma, b >0$. 
Let $\psi$ be a branching mechanism which is close to a function of the form
$\widetilde{\psi}(z)=-\alpha z +\rho z^2+ \eta z^{1+\beta}$ with $\alpha>0$, $\rho\ge 0$, $\eta>0$ and $\beta\in (0, 1)$, in some sense. In this paper, we study asymptotic behaviors of 
$(\xi, \psi)$-superprocesses $(X_t)_{t\geq 0}$.

@@

@@

@@

@@

@@

	We refer to $\pi$ as the \emph{L\'evy measure} of the branching mechanism $\psi$.

@@

    We say a real-valued Borel function $f:(t,x)\mapsto f(t,x)$ on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if for each $t\in \mathbb R_+$, we have

@@

       We say that an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ 

@@

    Recently, there have been quite a few papers on laws of large numbers for superdiffusions. In \cite{Englander2009Law, EnglanderWinter2006Law, EnglanderTuraev2002A-scaling}, some weak laws of large numbers (convergence in law or in probability) were established. The strong law of large numbers for superprocesses was first studied in \cite{ChenRenWang2008An-almost}, 
    followed by \cite{ChenRenSongZhang2015Strong-law, ChenRenYang2019Skeleton, EckhoffKyprianouWinkel2015Spines,KouritzinRen2014A-strong,LiuRenSong2013Strong, Wang2010An-almost} under different settings. 
    For a good survey on recent developments in laws of large numbers for branching Markov processes and superprocesses, see \cite{EckhoffKyprianouWinkel2015Spines}.

%    The strong law of large numbers of the above super-OU process $X$ can be stated as follows: 
   The strong law of large numbers for the super-OU process $X$ can be stated as follows:
    Under some conditions on the branching mechanism $\psi$ (these conditions are satisfied under our Assumptions 1 and 2 below), there exists an $\Omega_0$ of $\mathbb{P}_\mu$-full probability for every $\mu\in\mathcal M(\mathbb R^d)$ such that on $\Omega_0$, 
    for every Lebesgue-almost everywhere continuous bounded non-negative function $f$ on $\mathbb R^d$, 
    we have
%    $\lim_{t\to\infty}e^{-\alpha t}\langle f, X_t\rangle=H_\infty\langle f,\phi_0\varphi\rangle $, 
    $\lim_{t\to\infty}e^{-\alpha t}\langle f, X_t\rangle=H_\infty\langle f, \varphi\rangle $, 
    where $H_\infty$ is the limit of the non-negative martingale $e^{-\alpha t}\langle 1,X_t\rangle$ and 
%    $\phi_0$, $\varphi$ are functions which will be introduced in  \eqref{eigenfunction} and \eqref{invariantdensity} below.
$\varphi$ is the invariant density of the OU process $\xi$ defined in \eqref{invariantdensity} below.
    See \cite[Theorem 2.13 \& Example 8.1]{ChenRenYang2019Skeleton} and \cite[Theorem 1.2 \& Example 4.1]{EckhoffKyprianouWinkel2015Spines}.

    In this paper, we will establish some spatial central limit theorems (CLT) for the super-OU process $X$ above. 
    Our key assumption is that the branching mechanism $\psi(z)$ takes the form of $-\alpha z +\rho z^2+ \psi_1(z)$, where $\psi_1$ is close to $\eta z^{1+\beta}$ with $\eta>0$ and $\beta\in (0, 1)$, in some sense.
    We want to find
    $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ such that
\[
    \frac{\langle f, X_t \rangle -G_t}{F_t}
\]
    converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, 
    for some testing functions $f$.
%    It turns out that there are three regimes of different behavior of this CLT 
    It turns out that the statements of the CLT are different in three regimes
    depending on the sign of $\alpha\beta-\kappa_f b (1+\beta)$: the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$; the critical branching rate regime $\alpha\beta = \kappa_f b(1+\beta)$; and the large branching rate regime $\alpha\beta > \kappa_f b(1+\beta)$. Here, $\kappa_f$ is the order of $f$ in the spectral decomposition in terms of the spectrum of $L$. 
    Note that, in the setting of this paper, $\langle f,X_t\rangle$ typically have infinite second moment.

    There are many papers studying central limit theorems for branching processes, branching diffusions and superprocesses under the second moment condition.
    See
    \cite{Heyde1970A-rate, HeydeBrown1871An-invariance, HeydeLeslie1971Improved} for supercritical Galton-Watson processes, 
    \cite{KestenStigum1966Additional,KestenStigum1966A-limit} for supercritical multi-type Galton-Watson processes,
    \cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some} for supercritical multi-type continuous time branching processes and \cite{AsmussenHering1983Branching} for general supercritical branching Markov processes under certain conditions.
    In \cite{AdamczakMilos2015CLT}, 
    Adamczak and Milo\'s 
    proved some central limit theorems for supercritical branching Ornstein-Uhlenbeck processes with binary branching mechanism and in \cite{Milos2012Spatial} Milo\'s proved some central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition.
    These two papers made connections between the CLT and 
    %what they call branching rate regimes.
    the branching rate regimes
    In \cite{RenSongZhang2014Central}, Ren, Song and Zhang proved some central limit theorems for supercritical super-OU processes with branching mechanisms satisfying only a second moment.
    Moreover,
    compared with the results of \cite{AdamczakMilos2015CLT,Milos2012Spatial}, the limit distributions in \cite{RenSongZhang2014Central} are non-degenerate.
    In \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central},
    Ren, Song and Zhang also established a series of central limit theorems for a large class of general supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms.
    The functional version of the central limit theorems was established in \cite{Janson2004Functional} for supercritical multitype branching processes, and  in \cite{RenSongZhang2017Functional} for supercritical superprocesses.

    There are also many limiting theory for branching processes and branching Markov processes with branching mechanisms of infinite second moments.
    Heyde \cite{Heyde1971Some} established a central limit type  theorem for Galton-Watson process 
when the offspring distribution
    belongs to the domain of attraction of a stable law of index $\alpha\in (1, 2]$,
    and   proved that the limit law is  a stable law. Similar results  for supercritical multi-type Galton-Watson processes and supercritical  continuous time branching processes,  
under some $p$-th ($p\in(1,2]$) moment condition on the offspring distribution,
    were given in Asmussen \cite{Asmussen76Convergence}.
    Recently,   Marks and Milo\'s \cite{MarksMilos2018CLT}
    considered the limit behavior of supercritical branching Ornstein-Uhlenbeck processes with a special stable branching law. 
%    They established some central limit theorems in small and critical branching rate regimes, 
   They established some central limit theorems in the small and critical branching rate regimes, 
    but they did not prove any central limit theorem type result in the large branching rate regime.
    We also mention here that very recently \cite{IksanovKoleskoMeiners2018Stable-like} considered stable fluctuations of Biggins' martingales in the context of branching random walks and \cite{RenSongSun2018Limit} considered the asymptotic behavior of a class of critical superprocesses with spatially dependent stable branching.

    As far as we know, this paper is the 
%    first one in the literature on establishing CLT 
   first to study spatial central limit theorems
    for supercritical superprocesses without the second moment condition.

\subsection{Main results}
\label{sec: main results}{}

	We will always assume that the following Assumption holds.
\begin{asp}
\label{asp: Greys condition}
	The branching mechanism satisfies Grey's condition, i.e. there exists $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$ and  $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
\end{asp}
    For each $\mu \in \mathcal M(\mathbb R^d)$, write $\|\mu\| = \langle 1, \mu\rangle$.
	It is known (see \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations} for example) that, under Assumption \ref{asp: Greys condition}, 
	the \emph{extinction event} 
	$D:=\{\exists t\geq 0,~\text{s.t.}~\|X_t\|=0\}$ has positive probability, with respect to $\mathbb P_\mu$ for each  $\mu \in \mathcal M(\mathbb R^d)$.
    In fact,
\begin{equation}
    \mathbb{P}_{\mu} (D)
    = e^{-\bar v \|\mu\|},
    \quad \mu\in \mathcal M(\mathbb R^d),
\end{equation}
    where
\[
	\bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\} \in (0,\infty)
\]
	is the largest root of $\psi$.

    Denote by $\Gamma$ the gamma function.
For any $\sigma$-finite signed measure $\mu$, we use $|\mu|$ to denote the total variation measure of $\mu$. 
    In this paper, we will also assume the following:
\begin{asp}
\label{asp: branching mechanism}
    There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that
\begin{equation}
\label{eq: asp of branching mechanism}
    \int_{(1,\infty)}y^{1+\beta +\delta}~\Big|\pi(dy)-\frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| <\infty,
\end{equation}
	for some $\delta > 0$.
\end{asp}
	We will show in Subsection \ref{sec: branching mechanism} that if Assumption \ref{asp: branching mechanism} holds, then $\eta$ and $\beta$ are uniquely determined by the L\'evy measure $\pi$.
	In the reminder of the paper, we will always use $\eta,\beta$ to denote the constants corresponding to $\pi$.
\begin{rem}
\label{rem: small enough delta}
	Note that $\delta$ is not uniquely determined by $\pi$.
	In fact, if $\delta>0$ is a constant such that \eqref{eq: asp of branching mechanism} holds, then replacing $\delta$ by any smaller positive number, \eqref{eq: asp of branching mechanism} still holds.
	Therefore, Assumption \ref{asp: branching mechanism} is equivalent to the following statements: There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that, for each small enough $\delta>0$, \eqref{eq: asp of branching mechanism} holds.
\end{rem}

    Assumption \ref{asp: branching mechanism} says that 
 there exist constants $\eta>0$ and $\beta > 0$ 
    such that the L\'evy measure $\pi(dy)$ is not too far away from the measure $\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy$.
    In particular, if $\pi(dy)$ is equal to $\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy$, then the branching mechanism $\psi(z)$
    takes the form of
	$-\alpha z + \rho z^2 + \eta z^{1+\beta}$.
	It will be proved in Lemma \ref{lem: LlogL criterion} that, under Assumption 
	\ref{asp: branching mechanism}, the branching mechanism $\psi$ satisfies the 
	%$L \log L$ criteria, i.e.,
	$L \log L$ condition, i.e.,
\[
	\int_{(1,\infty)} y\log y~\pi(dy) < \infty.
\]
    This guarantees that $H_\infty$, the limit of the non-negative martingale $(e^{-\alpha t} \|X_t\|)_{t\geq 0}$, is non-degenerate.

    Denote by $\mathcal B(\mathbb R^d, \mathbb R)$ the space of all $\mathbb R$-valued Borel functions on $\mathbb R^d$.
    Denote by $\mathcal B(\mathbb R^d, \mathbb R_+)$ the space of all $\mathbb R_+$-valued Borel functions on $\mathbb R^d$.
    We use  $(P_t)_{t\geq 0}$ to denote the transition semigroup of $\xi$.	
    Define
\begin{equation}
\label{eq: meansemigroup}
    P^{\alpha}_t f(x)
    :=
    e^{\alpha t} P_t f(x) =
    \Pi_x [e^{\alpha t}f(\xi_t)],
    \quad x\in \mathbb R^d,t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+).
\end{equation}
    It is known that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$, in the sense that
\begin{equation}
    \mathbb{P}_{\mu}[\langle f, X_t \rangle]
    = \langle P^\alpha_t f, \mu \rangle,
    \quad t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+), \mu \in \mathcal M(\mathbb R^d).
\end{equation}
        The limiting behavior of the super-OU process is closely related to the asymptotic property of this mean semigroup $(P^\alpha_t)_{t\geq 0}$, and therefore, to the property of the OU semigroup $(P_t)_{t\geq 0}$.
